---
title: "coronavirus"
author: "Du"
date: "2026-03-12"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(dplyr)
library(readr)
library(ggplot2)

d_coronavirus <- read_csv('../data/life-under-lockdown-wave2-extract.csv')

```

# Hypothesis
H1 Gender is associated with number of conspiracy beliefs about coronavirus
H2 Age is associated with number of conspiracy beliefs regarding coronavirus
H3 Reliance on Facebook for information about coronavirus is associated with number of conspiracy beliefs regarding coronavirus

# Findings
## Hypothesis 1
```{r}
d_coronavirus %>%
 group_by (gender) %>%
 summarise(
	 n = n(), 
	 M = mean (beliefs), 
	 Mdn = median (beliefs),
	 Sd = sd (beliefs)
	)
```
```{r}
d_coronavirus %>%
  filter (gender != 'In another way') %>%
  t.test (beliefs ~ gender, data = .)
```
Males in the sample believed in more conspiracy theories than females, but this was not statistically significant, t(494.31) = -1.201, p = .230.

## Hypothesis 2
```{r}
 d_coronavirus %>%
  ggplot(
    aes(
      x = age,
      y = beliefs
    )
  ) + 
  geom_jitter()
```
```{r}
 d_coronavirus %>%
  cor.test( 
    ~ beliefs + age,
    data = .
    )
```
Age is negatively associated with number of conspiracy beliefs about coronavirus, r(498) = .24, p < .001.




## Hypothesis 3
```{r}
knowledge_levels <- c(
  'Nothing at all',
  'Not very much',
  'A fair amount',
  'A great deal')

d_coronavirus <- d_coronavirus %>%
  mutate(
    know_facebook = know_facebook %>%
      ordered(
        levels = knowledge_levels
        
      )
  )

  d_coronavirus %>%
  ggplot(
    aes(
      x = know_facebook,
      y = beliefs
    )
  ) +
  geom_violin()
```

```{r}
d_coronavirus <- d_coronavirus %>%
  mutate(
    know_facebook_coded = know_facebook %>%
      as.numeric
  )

d_coronavirus %>%
  cor.test(
    ~ beliefs + know_facebook_coded,
    data = .,
    method = 'spearman'
  )
```

reliance on facebook for knowledge of coronavirus is positively associated with number of conspiracy beliefs about coronavirus, rs(498) = .23, p < .001